Predictive modeling with cross validation

### 2017-08-23 model fitting/cross_validation.Rmd
wrote function to average performance metrics

```{r, echo = FALSE}
# function to perform cross validation + compute performance metrics
cv_allsplines <- function(train, test) {

  # building model on training data set
  model <- survival::coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(text_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train)

  # performance metrics for training data 
  train[["predictions"]] <- predict(model, type = "risk")
  metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train)
  train_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = round(metric$stats[3],2), 
                              pval = round(metric$stats[5],2), 
                              Dxy = round(metric$stats[9],2), 
                              AIC = stats::AIC(metric, k = 2), 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train)$concordance)

  # computing performance metrics 
  metric1 <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = test)
  test_metrics <- data.frame(HR = exp(metric1$coefficients), 
                             LR = round(metric1$stats[3],2), 
                             pval = round(metric1$stats[5],2), 
                             Dxy = round(metric1$stats[9],2), 
                             AIC = stats::AIC(metric1, k = 2), 
                             Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = test)$concordance)

  # returns data frame with train/test metrics 
  statistics <- rbind(train_metrics, test_metrics)
  rownames(statistics) <- c("Training Data", "Test Data")
  return(statistics) 
}

trains <- list(train1, train2, train3, train4, train5)
tests <- list(test1, test2, test3, test4, test5)

allspline_models <- purrr::map2(trains, tests, ~cv_allsplines(.x, .y))
allspline_models
# 5th iteration: pvalue for loglikelihood ratio test = 0.51 on test data 
```

@@

@@

```{r}
splinedev_avg <- get_avgmetrics(splinedev)
splinetext_avg <- get_avgmetrics(splinetext)
splinetag_avg <- get_avgmetrics(splinetag)
splinenew_avg <- get_avgmetrics(splinenew)
```

>>>>

```{r, echo = FALSE}
trains <- list(train1, train2, train3, train4, train5)
tests <- list(test1, test2, test3, test4, test5)

allvars <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = 'AIC') + pspline(text_length, df = 0, method = 'AIC') + pspline(avg_tag_length, df = 0, method = 'AIC')"
allsplines <- purrr::map2(trains, tests, ~crossval(allvars, .x, .y))

allsplines
# 5th iteration: pvalue for loglikelihood ratio test = 0.51 on test data 
```

@@

##### with splines on device_length and text_length

* splines on device_length and text_length ahd the most signficant p-values out of all splines in univariate analysis

```{r}
devtextvars <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = 'AIC') + pspline(text_length, df = 0, method = 'AIC')"

devtext <- purrr::map2(trains, tests, ~crossval(devtextvars, .x, .y))

```{r}
sqrtdev <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + sqrt(device_length) + pspline(text_length, df = 0, method = 'AIC')"

sqrtdev <- purrr::map2(trains, tests, ~crossval(sqrtdev, .x, .y))
sqrtdev

sqrttext <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + sqrt(text_length) + pspline(device_length, df = 0, method = 'AIC')"

sqrttext <- purrr::map2(trains, tests, ~crossval(sqrttext, .x, .y))

##### without splines

```{r}
vars <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday"

nospline <- purrr::map2(trains, tests, ~crossval(vars, .x, .y))
```

@@

```{r}
allspline_avg <- get_avgmetrics(allsplines)
splinedev_avg <- get_avgmetrics(splinedev)
splinetext_avg <- get_avgmetrics(splinetext)
splinetag_avg <- get_avgmetrics(splinetag)
splinenew_avg <- get_avgmetrics(splinenew)
nospline_avg <- get_avgmetrics(nospline)
devtext_avg <- get_avgmetrics(devtext)
sqrtdev_avg <- get_avgmetrics(sqrtdev)
sqrttext_avg <- get_avgmetrics(sqrttext)

allspline_avg; splinedev_avg; splinetext_avg; splinetag_avg; splinenew_avg; nospline_avg; devtext_avg; sqrtdev_avg; sqrttext_avg
```

```{r}
get_avgdiff <- function(list) {
  list_diff <- purrr::map(1:length(list), ~diff(as.matrix(list[[.]], lag = 1)))
  df <- plyr::ldply(list_diff, data.frame) %>%
    select(HR, Dxy, Concordance) %>%
    colMeans()
  return(df)
}

list <- list(allsplines, splinedev, splinetext, splinetag, splinenew, nospline, devtext, sqrtdev, sqrttext)
names <- c("allsplines", "splinedev", "splinetext", "splinetag", "splinenew", "nospline", "devtext", "sqrtdev", "sqrttext") # change this to avoid hard coding

l_diff <- purrr::map(list, ~get_avgdiff(.))
df_diff <- plyr::ldply(purrr::map(1:length(l_diff), ~data.frame(as.list(l_diff[[.]]))), data.frame)
rownames(df_diff) <- names
df_diff

#least amount of average change found in model with only the spline on newline_ratio 
```
